---
title: "Матрицы"
author: "Sofi Tormasheva"
date: "04 03 2017"
output:
  html_document: default
  pdf_document: default
---

Загружаем базу
```{r, warning=FALSE, error=FALSE, message=FALSE}
library(readr)
SpeedDating <- read_csv("~/pr3/project1/SpeedDating.csv")
```

Матрица для поиска похожих
```{r, warning=FALSE, error=FALSE, message=FALSE}
library(dplyr)
SD1 = select(SpeedDating, iid, age, gender, career_c, sports, tvsports, exercise, dining, museums, art, hiking, gaming, clubbing, reading, tv, theater, movies, concerts, music, shopping, yoga, attr3_1, sinc3_1, intel3_1, fun3_1, amb3_1, mn_sat)
```

Оставляем уникальных людей
```{r, warning=FALSE, error=FALSE, message=FALSE}
SD1un = unique(SD1)
SD1NA = na.omit(SD1un) #199
```
Предложение - исключить параметр mn_sat из-за малого количества данных
```{r, warning=FALSE, error=FALSE, message=FALSE}
SD2 = select(SpeedDating, iid, age, gender, career_c, sports, tvsports, exercise, dining, museums, art, hiking, gaming, clubbing, reading, tv, theater, movies, concerts, music, shopping, yoga, attr3_1, sinc3_1, intel3_1, fun3_1, amb3_1)
```

```{r, warning=FALSE, error=FALSE, message=FALSE}
SD2un = unique(SD2)
SD2NA = na.omit(SD2un)#535
```

535 уникальных человека в базе

База с расширенными личными характеристиками
```{r, warning=FALSE, error=FALSE, message=FALSE}
SD22 = select(SpeedDating, iid, gender, age, field_cd, race, imprace, imprelig, zipcode, goal, date, go_out, career_c, sports, tvsports, exercise, dining, museums, art, hiking, gaming, clubbing, reading, tv, theater, movies, concerts, music, shopping, yoga, exphappy, attr3_1, sinc3_1, intel3_1, fun3_1, amb3_1 )
```

```{r, warning=FALSE, error=FALSE, message=FALSE}
SD22un = unique(SD22)
SD22NA = na.omit(SD22un)#466
```

466 уникальных человека с расширенными характеристиками

Матрица решений dec бинарность
```{r}
SDFdec = select (SpeedDating, iid, pid, dec)
SDFdec = na.omit(SDFdec) #8368
SDFdec$dec=as.numeric(SDFdec$dec)
```

Матрица решений like шкала 0-10
```{r}
SDFlike = select (SpeedDating, iid, pid, like)
SDFlike = na.omit(SDFlike) #8128
SDFlike$like = as.numeric(SDFlike$like)
```

```{r}
SDFlike7= filter(SDFlike, like>7) #1885
```

```{r}
SDFdec1 = filter(SDFdec, dec>0) #3515
```

iid - уникальный номер
age - возраст
gender - пол
career_c - закодированная карьерная область
1= Lawyer
2= Academic/Research
3= Psychologist
4= Doctor/Medicine
5=Engineer
6= Creative Arts/Entertainment
7= Banking/Consulting/Finance/Marketing/Business/CEO/Entrepreneur/Admin
8= Real Estate
9= International/Humanitarian Affairs
10= Undecided
11=Social Work
12=Speech Pathology
13=Politics
14=Pro sports/Athletics
15=Other
16=Journalism
17=Architecture

Интересы:
sports: Playing sports/ athletics
tvsports: Watching sports
exercise: Body building/exercising
dining: Dining out
museums: Museums/galleries
art: Art
hiking: Hiking/camping
gaming: Gaming
clubbing: Dancing/clubbing
reading: Reading
tv: Watching TV
theater: Theater
movies: Movies
concerts: Going to concerts
music: Music
shopping: Shopping
yoga: Yoga/meditation

Личные характеристики:
attr3_1 Attractive
sinc3_1 Sincere
intel3_1 Intelligent
fun3_1 Fun
amb3_1 Ambitious

field_cd закодированный field of study
1= Law
2= Math
3= Social Science, Psychologist
4= Medical Science, Pharmaceuticals, and Bio Tech
5= Engineering
6= English/Creative Writing/ Journalism
7= History/Religion/Philosophy
8= Business/Econ/Finance
9= Education, Academia
10= Biological Sciences/Chemistry/Physics
11= Social Work
12= Undergrad/undecided
13=Political Science/International Affairs
14=Film
15=Fine Arts/Arts Administration
16=Languages
17=Architecture
18=Other

race
Black/African American=1
European/Caucasian-American=2
Latino/Hispanic American=3
Asian/Pacific Islander/Asian-American=4
Native American=5
Other=6

imprace:
How important is it to you (on a scale of 1-10) that a person you date be of the same
racial/ethnic background?
imprelig:
How important is it to you (on a scale of 1-10) that a person you date be of the same
religious background?
zipcode:
What was the zip code of the area where you grew up?

goal:
What is your primary goal in participating in this event?
Seemed like a fun night out=1
To meet new people=2
To get a date=3
Looking for a serious relationship=4
To say I did it=5
Other=6

date:
In general, how frequently do you go on dates?
Several times a week=1
Twice a week=2
Once a week=3
Twice a month=4
Once a month=5
Several times a year=6
Almost never=7

go out:
How often do you go out (not necessarily on dates)?
Several times a week=1
Twice a week=2
Once a week=3
Twice a month=4
Once a month=5
Several times a year=6
Almost never=7

career_c: career coded
1= Lawyer
2= Academic/Research
3= Psychologist
4= Doctor/Medicine
5=Engineer
6= Creative Arts/Entertainment
7= Banking/Consulting/Finance/Marketing/Business/CEO/Entrepreneur/Admin
8= Real Estate
9= International/Humanitarian Affairs
10= Undecided
11=Social Work
12=Speech Pathology
13=Politics
14=Pro sports/Athletics
15=Other
16=Journalism
17=Architecture

exphappy:
Overall, on a scale of 1-10, how happy do you expect to be with the people you meet
during the speed-dating event?
